Trauma treatment delay

### 2023-12-01 manuscriptlongversion.Rmd
text

The results show that generally, patients do not systemically receive
delayed treatment because of a patient level factor. In both groups, ISS
had an unadjusted odds ratio of 0.98 and 0.96 respectively. The
disparity between these ORs is because of previously mentioned slightly
different group sizes and patients because of the different patients
being excluded.

As we see in the results, there were two variables that, when adjusted,
had a correlation with the risk for a patient of receiving delayed
treatment, one being the highest hospital care level. Compared with
having the ER as the highest care level, patients who were in the ICU or
the OR had a substantially lowered chance of receiving delayed
treatment. This can be attributed to

The other variable that when adjusted for had a correlation with
receiving delayed treatment was getting a emergency procedure. Compared
to not receiving an emergency measure, all observed emergency procedures
had a correlation with lower chance of delayed treatment. This can be
attributed to

@@

The above shown results should be seen as a good thing, as it suggests
that the delayed treatment happens more at random than because of a
factor on a patient level.

>>>>

These results show that there seems to be a correlation between some
variables and the presence of delayed treatment. A higher GCS had a
correlation with delayed treatment while a lower ISS had the same
correlation. This suggests that a less injured and more awake patient
has a higher risk of receiving delayed treatment. Compared to previous a
previous study analysing the same data but with ofi as the outcome, this
result is surprising as that study came to the opposite result
[@Pat_factors]. This can possibly be explained by that the study looked
at all ofi, whereas this study concentrates on delayed treatment.
Delayed treatment might have this correlation because an injured and
unconscious patient might receive more attention at the hospital,
leading to fewer instances delays compared to a patient that seems less
injured.

@@
